Identifying regime transitions for water governance at a basin scale

### 2022-04-26 paper/main/01_introduction.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

\label{Intro.}
Water has been described as being ``at the centre of the planetary drama of the Anthropocene''
\cite{gleesonIlluminatingwatercycle2020}.
It is essential not only for earth system processes but also in supporting the economic development and continued well-being of human societies. Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, moving rivers dominated by a hybrid of social and natural tendencies
\cite{gleesonIlluminatingwatercycle2020,sivapalanSociohydrologynewscience2012,qinTheoreticalframeworkdualistic2014,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
Facing this major transformation, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
\cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}.
As an integral part of a proposed earth system governance framework, water governance requires a deep understanding of changes in the complex relationships between humans and water
\cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.

Governance is essentially about ``who gets what, when and how''. Specifically, water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %! citation.
For water resources in populated areas, missing governance means missing sustainability, and a first important step in understanding transitions toward successful water governance is identifying the different regimes.
\cite{undpwatergovernancefacilityWaterGovernanceIssue}.
Corresponding to ``who gets what, when and how'', the United Nations Development Programme (UNDP) suggests three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (supply), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
As a locally stable state of a system, function, and dominant controls, habitual relationships between humans and water maintain regimes of water governance
\cite{carpenterEarlyWarningsRegime2011}.
However, large and persistent changes in key properties may lead to a loss of systematical stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
\cite{rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts can trigger changes in the three key dimensions of water governance (supply, purpose, and allocation), with new challenges to sustainability %! UNDP year
\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
First, the supply of water depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
\cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
\cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
Third, the allocation of water across the whole basin is influenced not only by regionally socio-economic and environmental context but also by systematically regulating resources
\cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.
The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).

As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details), the fifth-largest river in the world.
With drastically anthropogenic intervention, the YRB experienced the most intense water governance challenges in China, leading to long-standing sustainability barriers.
Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
\cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
However, water over-use has led to depletions of the over-burdened river, creating new governance challenges that have been addressed through a range of related policies (e.g., regulating water use and limiting water withdrawals)
\cite{xiaDevelopmentWaterAllocation2012}.
Today, it is still impossible to completely cover water demands, balance trade-offs between ecosystem services, and lead to equities in different regions; -who gets water, when and how is still an open question for sustainable water governance
\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
The YRB has been among the most rapidly-changing large river basins worldwide, with myriad responses to the endless governance challenges induced by environmental, economic, social and political factors. Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, we first use the three key dimensions (supply, purpose and allocation) by corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
% 使用案例研究
Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated regimes of water governance and their leading causes in a comprehensive but straightforward way.
% 最后总结出一般性框架
Finally, we propose a general regime transition scheme as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.

\begin{figure*}%[htbp]
	%! I don't know that fig.1 adds much, the explanatory text to the figure is the key.
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.jpg}
	\caption{
		A framework for understanding the relationship between water governance regimes and transitions of a hydrosocial cycle. We aim to detect regime shifts using a simple and comprehensive index.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A:} there are three key dimensions (supply, purpose and allocation) of water governance (see \textbf{Methods} for details). Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance. (2) ``purpose'' is weighted between consumptive services or non-consumptive uses. (3) ``allocation'' changes between balanced or lopsided.
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B:} along a trajectory of hydrosocial water cycle, governance changes are related to the combination of trends across the three dimensions. When abrupt change occurs, it may indicate a regime shift in water governance
		\cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
	}
	\label{fig:framework}
\end{figure*}

>>>>

\label{Intro.}
Water, being ``at the centre of the planetary drama of the Anthropocene'' \cite{gleesonIlluminatingwatercycle2020}, is essential not only for earth system processes but also in supporting the economic development and human well-being.
Human activities stemming from our reliance on the water have profoundly modified the natural water cycle, resulting in rivers dominated by a hybrid of social and natural tendencies
\cite{gleesonIlluminatingwatercycle2020,sivapalanSociohydrologynewscience2012,qinTheoreticalframeworkdualistic2014,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
Facing this transition, many big river basins worldwide (which are hot spots of civilization and economic growth) are urgently in need of successful water governance for sustainability
\cite{bestAnthropogenicstressesworld2019,falkenmarkUnderstandingwaterresilience2019,dibaldassarreSociohydrologyScientificChallenges2019}.
As an integral part of a proposed earth system governance framework, water governance requires a deep understanding of changes in the complex relationships between humans and water
\cite{dibaldassarreSociohydrologyScientificChallenges2019,biermannNavigatingAnthropoceneImproving2012,steffenemergenceevolutionEarth2020}.

Governance is essentially about ``who gets what, when and how''. Specifically, water governance refers to the political, social, economic, and administrative systems that influence the use and management of water %! citation.
For water resources in populated areas, missing governance means missing sustainability, and a first important step in understanding transitions toward successful water governance is identifying the different regimes.
\cite{undpwatergovernancefacilityWaterGovernanceIssue}.
Corresponding to ``who gets what, when and how'', the United Nations Development Programme (UNDP) suggests three key dimensions of water use are decided by the water governance directly: ``When and what water to use?'' (stress), ``How water provides different services to well-beings?'' (purpose), and ``Who can use water equally and efficiently?'' (allocation)
\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.

As a temporary stable state in structure, function, and dominant controls, a specific regime of water governance maintains by concreted intertwines within human-water systems (such as management, institutions, and exploitations)
\cite{carpenterEarlyWarningsRegime2011}.
However, large and persistent changes in key properties may lead to a loss of systematical stability, potentially resulting in a regime shift with impacts on system outcomes and widespread cascading effects
\cite{rochaCascadingregimeshifts2018, gregrCascadingsocialecologicalcosts2020}.
Therefore, as both signals and consequences of substantive changes in human-water systems, regime shifts align with changing three key dimensions of water governance (stress, purpose, and allocation), sometimes leading to new challenges in sustainability %! UNDP year
\cite{undpwatergovernancefacilityWaterGovernanceIssue, mariajacobsonUserguideassessing2013, kjellenWatergovernanceperspective2015}.
First, water stress depends not only on climate (with increasing scarcity and uncertainty in many regions) but also on the increasingly insatiable demands from economic activities such as irrigation and industry; water storage can resolve some but not all of these issues
\cite{greveGlobalassessmentwater2018,wadaHumanwaterinterface2017,qinFlexibilityintensityglobal2019}.
Second, the purpose of how water services human well-being is to consider trade-offs between consumptive uses (e.g., drinking and food production) and non-consumptive uses (e.g., energy production)
\cite{liuWaterscarcityassessments2017,florkeWatercompetitioncities2018,kleemannQuantifyinginterregionalflows2020}.
Third, the allocation of water across the whole basin is influenced not only by regionally socio-economic and environmental context but also by systematically regulating resources
\cite{roobavannanRoleSectoralTransformation2017,speedBasinwaterallocation2013}.
Despite regime shifts in water governance related to substantive changes in any of the three dimensions, separately considering their intertwines within human-water systems can lead to holistic failure in governing water.
The lack of a comprehensive but straightforward approach to identifying changes in water governance regimes challenges sustainability, and filling this gap can well align human and water systems (Figure~\ref{fig:framework}).

As an informative example, we focus on the Yellow River Basin (YRB, see \textit{Appendix} Methods S1 and Figure S1 for details), the fifth-largest river in the world.
With drastically anthropogenic intervention, the YRB experienced the most intense water governance challenges in China, leading to long-standing sustainability barriers.
Since the 1960s, the implementation of conservation measures, regulation reservoirs, and levee constructions have contained the issues caused by high-sediment loads
\cite{wangReducedsedimenttransport2016,wuEvolutioneffectssocialecological2020}.
However, water over-use has led to depletions of the over-burdened river, creating new challenges and new governance practices, including water use regulation and water transfer across basins
\cite{xiaDevelopmentWaterAllocation2012}.
Today, it is still impossible to completely solve water stress, trade-offs between ecosystem services, or lopsided development in different regions in the YRB; -``who gets water, when and how‘’ is still an open question for sustainable water governance
\cite{wangYellowRiverwater2019,wohlfartSocialecologicalchallengesYellow2016}.
However, confronting governance challenges induced by environmental, economic, social, and political factors, numerous governance practices have led the YRB to be among the most drastically-governing large river basins worldwide
Identifying regime shifts in water governance within the YRB can thus provide crucial insights into rapidly-changing big river basins and how governance may respond to meeting challenges to their sustainability.

% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, we use the three core dimensions (stress, purpose and allocation) and corresponding indicators of water governance to develop an Integrated Water Governance Index (IWGI) that can detect and describe changes in water governance at a basin-scale (see Figure~\ref{fig:framework} and methods).
% 使用案例研究
Then, by applying the index to a typical rapid-changing big river basin (the YRB), we show how to analyze the complicated regimes of water governance and their leading causes in a comprehensive but straightforward way.
% 最后总结出一般性框架
Finally, we propose a general regime transition schema as a practical guideline for a coordinated approach to exploring the challenges faced by big river basin governance.

\begin{figure*}%[htbp]

%! I don't know that fig.1 adds much, the explanatory text to the figure is the key.
	\centering
	\includegraphics[width=0.9\textwidth]{main/framework.png}
	\caption{
		A framework for identifying the water governance regimes and transitions of a hydrosocial cycle.
		\textbf{A:} water governance has three key dimensions (stress, purpose and allocation), each of which has two potential directions (denoted in red) when changing: (1) ``stress'' of water shifts between scarcity and abundance; (2) ``purpose'' of water is weighted between consumptive services or non-consumptive uses; (3) ``allocation'' changes between balanced or lopsided.
		\textbf{B:} along a transition of hydrosocial water cycle, water governance shifts in line with the three dimensions. By combining corresponding indicators, an abrupt change of the IWGI thus indicates a regime shift in water governance.
		% \cite{steffenTrajectoriesEarthSystem2018,abbottwatercycleAnthropocene2019,leviaHomogenizationterrestrialwater2020}.
	}
	\label{fig:framework}
\end{figure*}

### 2022-04-26 paper/main/02_methods.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
	\begin{itemize}
		%! Why ??? Explaination: why should development lead to balance among regions or meet the needs of different sectors.
		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
		\item \textbf{Supply($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals. However, since effective water governance may boost supply capacities to meet water demands by technical solutions in the process of development:
		\begin{equation}
			Transformation \propto S^{-1}
		\end{equation}

@@

	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, A or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to supply, purpose, and allocation respectively) for each dimension. Then, the above equation was transformed into a natural logarithm to facilitate calculation:
	\begin{equation}
		Transformation \propto ln(I_S) + ln(I_P) + ln(I_A)
	\end{equation}

@@

	\subsubsection*{Indicator of supply}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water supply capacities ($SFV_i$) as the indicator in a certain region $i$ \cite{qinFlexibilityintensityglobal2019}. This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details). For the whole YRB, the indicator of supply capacity $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

>>>>

	% - 社会的发展通常伴随着用水向社会经济系统倾斜，用水方式优先向收益更高的非供给性方式倾斜：
	\begin{itemize}
		%! Why ??? Explaination: why should development lead to balance among regions or meet the needs of different sectors.
		% - 可持续的社会发展应该通过技术手段有效缓解发展过程中产生的水资源压力，才能实现可持续发展：
		\item \textbf{Stress ($S$)}: Socio-economic dominance may lead to further demands on the water supply because of increasing water withdrawals. However, since effective water governance may boost supply capacities to meet water demands through technical solutions in the process of development:
		\begin{equation}
			Transformation \propto S^{-1}
		\end{equation}

@@

	% 在上述假设的基础上，我们要构建流域综合耦合指数(Integrated Water Resources governance, IWGI)，使 IWGI 有效表征与用水相关的三个维度。首先为每个维度选择一个合适的指示因子（indicator, $I_x$, 其中$x=P, A or S$）。将上式进行自然对数转换，从而让三个维度之间变成加减关系：
	To effectively represent the three dimensions, we selected an appropriate indicator ($I_x$, $x=S$, $P$ or $A$ corresponding to stress, purpose, and allocation respectively) for each dimension. Then, the above equation was transformed into a natural logarithm to facilitate calculation:
	\begin{equation}
		Transformation \propto ln(I_S) + ln(I_P) + ln(I_A)
	\end{equation}

@@

	\subsubsection*{Indicator of stress}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed in Qin et al., 2019 to evaluate water stress ($SFV_i$) as the indicator in a particular region $i$ \cite{qinFlexibilityintensityglobal2019}. This metric takes into account management measures (such as the construction of reservoirs) and the impact of changes in the industrial structure of water use on the evaluation of water scarcity (see \textit{SI Appendix} Methods S4 for details). For the whole YRB, the indicator of water stress $I_S$ is the average of all regions' SFV-index:
	\begin{equation}
		I_S = \frac{1}{4} * \sum_{i=1}^4 SFV_{i}
	\end{equation}

### 2022-04-26 paper/main/03_results.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/index.jpg}
	\caption{Changes in the IWGI index.
	\textbf{A,} Change points detection. With significant change points in 1978 and 1994, the IWGI has three different periods.
	\textbf{B,} Contributions of each dimension to the changes of IWGI within each of the three periods. Supply, purpose and allocation were the main positive contributors to P1, P2 and P3.
	\textbf{C,} Combination of contributions across three dimensions in different periods (S: supply; P: purpose; A: allocation).
	The red indicator line in this plot denotes a 1:1 contribution between purpose (P) and allocation (A). When the points are below this line, the contribution ratio of allocation is lower than that of function, and \textit{vice versa}.
	}
	\label{fig:IWGI}
\end{figure*}

% 这一节主要展示IWGI的变化趋势和WUR的划分
Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three dimensions (Figure~\ref{fig:IWGI}A).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI, the remarkable downward trend correlates significantly to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
% 第二阶段
In the second period (P2, 1979-2001), the increasing stress indicator significantly contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
% 第三阶段
During the third period (P3, 1995-2013), while the stress indicator kept its most significant share in contributions, the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.

% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
The ternary shows overall features of the three dimensions in different periods, where each regime shift is relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
% 第一阶段到第二阶段
Throughout P1, the IWGI shifts paralleled the left axis because the Purpose indicator barely changed, and the other two changed in similar trends.
Analogously, as the stress indicator is unchanged during the P3, the IWGI shifts paralleled with the right side of the axis while the other two changed in opposite trends.
% 第三阶段集中
The regime then experienced a long-distance shift during the P2, as three indicators simultaneously changed their contribution ratios to IWGI.
% 总结来说，三个稳态
The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and a demand regulating regime (P3: 2002-2013).

\subsection{Causes of water governance regime shifts}
\label{Res.2}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/causes.pdf}
	\caption{
		Causes of water governance regime shifts in the Yellow River Basin: environmental change, economic growth and efficiency changes, social transformation, and water governance policies.
		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the area, the green dot line), see \textit{SI Appendix} Methods S2).
		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line) (\textit{SI Appendix} Methods S2).
		\textbf{C.} Completed time of each new reservoir and their located region's (source, upper, middle, or lower reaches) water use percentages as a proportion of the basin's total water use (WU) at that time. Red circles denote the reservoirs mainly for managing and regulating the whole basin.
		The size of each circle indicates the magnitude of its water storage capacity. Some important reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which was constructed mainly for managing floodwater discharge and water supply. The named reservoirs are significant for the entire basin, not only for regional development.
		%! 不清楚D的这些圆圈代表啥
		\textbf{D.} Social transformations and national-level policies related to water governance (see \textit{SI Appendix} Methods S1 and Table S2). In order, the four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Allocation Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order (see \textit{SI Appendix} Methods S1).
	}
	\label{fig:Causes}
\end{figure*}

% 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
Digging more deeply into the underlying causes of changes in the IWGI, the expansion of irrigated areas and the economic growth of industry and services were critical to the change in purpose between P1 and P2.
% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
During P1, the area of irrigated agriculture in the Yellow River Basin expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig. S3).
% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
Entering P2, however, the expansion of irrigated area slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).

% 水分利用效率由P2变化到P3。
From P2 to P3, the efficiency of water use changed obviously.
Not only irrigated areas keep their slow expansion in P3 (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig. S4), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
As a result, the differences between sectors of water use reduced while the total water stress remained stable during P3 (\textit{SI Appendix} Fig. S3).

% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
Finally, environmental context, social transformation and policies played roles in all three regimes.
% 我们计算了每个水库的区域和盆地用水比例(R/B ratio)，较高的比例代表潜在的供水作用，而不是调节作用。
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
% 在自然水资源相对丰富的P1年，水库大多建在需水量高的地区，水库的需水量比显著偏高。
Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during P1 (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, p<0.01), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig. S5).
% 在P2中，新水库的数量显著减少，水量分配受到“87调水方案”的严格控制，总库容几乎没有增加(\textit{SI  Appendix}图S6)。
Since P2, the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, p<0.01 and \textit{SI Appendix} Fig. S6).
% 进入P3期后，以“环境监管”为指导的无数国家层面的水治理政策被提出，为了便于监管，新建的水库数量甚至更多，其中大部分建在R/B比较低的地区。
In P3, authorities proposed more national-level water governance policies under the guidance of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

>>>>

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/index.jpg}
	\caption{Changes in the IWGI index and corresponding water governance regimes: P1: 1965-1978, P2: 1979-2001, and P3: 2002-2013.
	\textbf{A,} detecting change points of IWGI and contributions from each indicator. Two significant change points ($p<0.01$) occurred in 1978 and 2001.
	\textbf{B,} correlation of trends between the IWGI and the indicators.
	\textbf{C,} across three indicators, changing components of the IWGI, whose directions shifts between different regimes.
	}
	\label{fig:IWGI}
\end{figure*}

% 这一节主要展示IWGI的变化趋势和WUR的划分
Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three dimensions (Figure~\ref{fig:IWGI}A).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, spectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
% 第二阶段
In the second period (P2, 1979-2001), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.
% 第三阶段
During the third period (P3, 1995-2013), while the stress indicator kept its biggest share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime of IWGI.

% 每个时期都有一个独特的、最引人注目的、对IWGI作出积极贡献的人。不同时期的三维总体特征如图所示。
The ternary shows overall features of the three dimensions in different periods, where each regime shift is relative to a directional change in the combination of three dimensions (Figure~\ref{fig:IWGI}C).
% 第一阶段到第二阶段
Throughout P1, the IWGI shifts paralleled the left axis because the Purpose indicator barely changed, and the other two changed in similar trends.
Analogously, as the stress indicator is unchanged during the P3, the IWGI shifts paralleled with the right side of the axis while the other two changed in opposite trends.
% 第三阶段集中
The regime then experienced a long-distance shift during the P2, as three indicators simultaneously changed their contribution ratios to IWGI.
% 总结来说，三个稳态
The three different periods corresponded to three distinct water governance regimes: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001), and an adaptation oriented regime (P3: 2002-2013).

\subsection{Causes of the regime shifts}
\label{Res.2}

\begin{figure*}[th!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/causes.pdf}
	\caption{
		Causes of water governance regime shifts in the YRB: environmental change, economic growth and efficiency changes, social transformation, and governance policies.
		\textbf{A.} Changes in the total irrigated area (orange line) and water use intensity ($WU/A$, water use divided by the area, the green dot line).
		\textbf{B.} Changes in gross values added (GVA) of industry and services (blue line) and their water use intensities ($WU/GVA$ WU divided by the GVA, the red dot line).
		\textbf{C.} Completed time of each new reservoir and their located region's water use (LWU) percentages as a proportion of the total basinal water use (BWU) at that time. Red circles denote the reservoirs mainly for managing and regulating the whole basin.
		The size of each circle indicates the magnitude of its water storage capacity. Some crucial reservoirs include (1) Xiaolangdi reservoir and Sanmen Reservoir, which were constructed mainly for managing sediments; and (2) Impoundments at Liujia Gorge, Longyang Gorge, which were constructed mainly for managing floodwater discharge and water regulation. These named reservoirs are significant for the whole basin rather than for local development.
		\textbf{D.} Social transformations (red triangles) and national-level governance policies (the circles, different colors denote signed by different state institution, see \textit{SI Appendix} Table S2). The lightgray bars year-by-year show frequency of official documents related to the YRB at a basinal scale (see \textit{SI Appendix} Table S3).
	}
	\label{fig:Causes}
\end{figure*}

% 进一步挖掘IWGI变化的根本原因，灌溉区扩张和工业和服务业的经济增长是P1和P2目的变化的关键。
Underlying causes of changes in the IWGI associates to various factors, but different in dominates of the two regime shifts. The expansion of irrigated areas and the economic growth of industry and services were critical to the change in purpose between P1 and P2.
% P1年，黄河流域灌溉农业面积以图A的速度快速扩张，灌溉用水占主导(1965年占总用水的$81.56\%$, 1978年占总用水的$83.17\%$，图S3)。
During the massive supply regime (P1), the area of irrigated agriculture in the YRB expanded rapidly at a rate of $0.25*10^6 ha/yr$ (Figure\ref{fig:Causes} A), and irrigation water was the dominant water use ($81.56\%$ of the total water use in 1965, and $83.17\%$ in 1978 \textit{SI Appendix} Fig. S3).
% 然而，进入P2后，灌溉区扩张停滞，工业和服务业逐渐增长，用水需求增加(图re\ref{fig: Causes} B)，导致灌溉用水量比例下降$8\%$ S3。
Entering the transformation governance regime (P2), however, the expansion of irrigated area slowed down, and industry and services gradually took off, with more water demands (Figure\ref{fig:Causes} A and B), leading to an $8\%$ reduction in the proportion of irrigation water use (\textit{SI Appendix} S3).

% 水分利用效率由P2变化到P3。
From P2 to P3, the efficiency of water use changed obviously.
Not only irrigated areas keep their slow expansion in the adaptation oriented regime (P3) (Figure\ref{fig:Causes}A), but industry and urban services also assumed a more vital economic role (represented by Gross Added Values, GVA) (Figure~\ref{fig:Causes}B).
However, because of more efficient technology and better water conservation practices (\textit{SI Appendix} Fig. S4), both experienced significant declines in water use for a unit irrigated area or unit production (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B).
As a result, the differences between sectors of water use reduced while the total water stress remained stable during P3 (\textit{SI Appendix} Fig. S3).

% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
Finally, environmental context, social transformation and policies played roles in all three regimes.
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
Under the guiding ethos of ``conquering nature'', most of the reservoirs were built in regions with high water demands during the massive supply regime (R/B ratios were significantly higher, see Figure~\ref{fig:Causes}C, $p<0.01$), when natural water resources were also relatively abundant (\textit{SI Appendix} Fig. S5).
Since the transformation governance regime (P2), the number of new reservoirs decreased significantly and significantly increased basinal policies rigorously controlled the allocation of water (e.g., the ``87 Water Allocation Scheme'') (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{SI Appendix} Fig. S6).
In the adaptation oriented regime, authorities proposed more national-level water governance policies under the guidance of national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.
